Analysis_exp7

### 2017-12-24 Traditional_Analysis/Analysis_exp7_2.rmd
try to ignore some
pull

pkgNeeded <- (c("ez","plyr","ggplot2", "reshape2", "MBESS", "bootES","BayesFactor","psych","corrplot"))

@@

```{r loadingData_e7_L,echo=FALSE,results='hide'}
df.L <- read.csv("df.Learn.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
df.T <- read.csv("df.Test.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
# render the numeric column
cols.num <- c("Age","Block","Bin","Trial","RT","Accuracy")
# Tcols.num <- c("SubjectID","Age","Block","Bin","Trial","RT","Accuracy")
df.L[cols.num] <- sapply(df.L[cols.num], as.numeric)
df.T[cols.num] <- sapply(df.T[cols.num], as.numeric)

@@

```{r clean the data_e7_L,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1 <- df.L
df.T1 <- df.T
df.L1$RT <- df.L1$RT*1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000

@@

the effect of self on ACC
The correlation of accuracy between matching task and categrization based on morality criteria
```{r correlation of self-effect on ACC between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
acc.self_bias_moral <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Valence_slf_oth_good)
df.acc.self_bias_moral <- df.corr.bias_acc[,c("L_acc_slf_oth_good","T_acc_Valence_slf_oth_good")]
colnames(df.acc.self_bias_moral) <- c("ACC_self_bias_match","ACC_self_bias_moral_categorization")
ggplot(df.acc.self_bias_moral, aes(x=ACC_self_bias_match, y=ACC_self_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between ACC of Matching and moral categorization (self-effect)") +
    apatheme
#ggsave("p_corr_acc_self1.eps", p_corr_acc_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_self1.pdf",out.type="cairo", width=8, height=6)
```

The correlation of accuracy between matching task and categrization based on identity criteria
```{r correlation of self-effect on ACC between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
acc.self_bias_id <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Id_slf_oth_good)
df.acc.self_bias_id <- df.corr.bias_acc[,c("L_acc_slf_oth_good","T_acc_Id_slf_oth_good")]
colnames(df.acc.self_bias_id) <- c("ACC_self_bias_match","ACC_self_bias_id_categorization")
ggplot(df.acc.self_bias_id, aes(x=ACC_self_bias_match, y=ACC_self_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between ACC of Matching and id categorization (self-effect)") +
    apatheme
#ggsave("p_corr_acc_self2.eps", p_corr_acc_self2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_self2.pdf",out.type="cairo", width=8, height=6)
```

The effect of morality 
The correlation of accuracy between matching task and categrization based on morality criteria
```{r correlation of moral-effect on ACC between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
acc.moral_bias_moral <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Valence_good_bad_slf)
df.acc.moral_bias_moral <- df.corr.bias_acc[,c("L_acc_good_bad_slf","T_acc_Valence_good_bad_slf")]
colnames(df.acc.moral_bias_moral) <- c("ACC_moral_bias_match","ACC_moral_bias_moral_categorization")
ggplot(df.acc.moral_bias_moral, aes(x=ACC_moral_bias_match, y=ACC_moral_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm,fill = "gray") +   
    ggtitle("Correlation between ACC of Matching and moral categorization (moral effect)") +
    apatheme
#ggsave("p_corr_acc_moral1.eps", p_corr_acc_moral1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_moral1.pdf",out.type="cairo", width=8, height=6)
```

The correlation of accuracy between matching task and categrization based on identity criteria
```{r correlation of moral-effect on ACC between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
acc.moral_bias_id <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Id_good_bad_slf)
df.acc.moral_bias_id <- df.corr.bias_acc[,c("L_acc_good_bad_slf","T_acc_Id_good_bad_slf")]
colnames(df.acc.moral_bias_id) <- c("ACC_moral_bias_match","ACC_moral_bias_id_categorization")
ggplot(df.acc.moral_bias_id, aes(x=ACC_moral_bias_match, y=ACC_moral_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm,fill = "gray") +   
    ggtitle("Correlation between ACC of Matching and id categorization (moral effect)") +
    apatheme
# ggsave("p_corr_acc_moral2.eps", p_corr_acc_moral2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_moral2.pdf",out.type="cairo", width=8, height=6)
```

```{r correlation of self-effect on RT between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
rt.self_bias_moral <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Valence_slf_oth_good)
df.rt.self_bias_moral <- df.corr.bias_rt[,c("L_rt_m.slf_oth_good","T_rt_Valence_slf_oth_good")]
colnames(df.rt.self_bias_moral) <- c("RT_self_bias_match","RT_self_bias_moral_categorization")
ggplot(df.rt.self_bias_moral, aes(x=RT_self_bias_match, y=RT_self_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between RT of Matching and moral categorization (self-effect)") +
    apatheme
#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_self1.pdf",out.type="cairo", width=8, height=6)
```

```{r correlation of self-effect on RT between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
rt.self_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Id_slf_oth_good)
df.rt.self_bias_id <- df.corr.bias_rt[,c("L_rt_m.slf_oth_good","T_rt_Id_slf_oth_good")]
colnames(df.rt.self_bias_id) <- c("RT_self_bias_match","RT_self_bias_id_categorization")
ggplot(df.rt.self_bias_id, aes(x=RT_self_bias_match, y=RT_self_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm,fill = "gray") +   
    ggtitle("Correlation between RT of Matching and id categorization (self-effect)") +
    apatheme
#ggsave("p_corr_RT_self2.eps", p_corr_RT_self2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_self2.pdf",out.type="cairo", width=8, height=6)

@@

```{r correlation of moral-effect on RT between matching and categorization of moral,echo=FALSE,warning=FALSE,message=FALSE }
rt.moral_bias_val <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Valence_good_bad_slf)
df.rt.moral_bias_moral <- df.corr.bias_rt[,c("L_rt_m.good_bad_slf","T_rt_Valence_good_bad_slf")]
colnames(df.rt.moral_bias_moral) <- c("RT_moral_bias_match","RT_moral_bias_moral_categorization")
ggplot(df.rt.moral_bias_moral, aes(x=RT_moral_bias_match, y=RT_moral_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between RT of Matching and moral categorization (moral-effect)") +
    apatheme
#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_moral1.pdf",out.type="cairo", width=8, height=6)
```

```{r correlation of moral-effect on RT between matching and categorization of id,echo=FALSE,warning=FALSE,message=FALSE }
rt.moral_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Id_good_bad_slf)
df.rt.moral_bias_id <- df.corr.bias_rt[,c("L_rt_m.good_bad_slf","T_rt_Id_good_bad_slf")]
colnames(df.rt.moral_bias_id) <- c("RT_moral_bias_match","RT_moral_bias_id_categorization")
ggplot(df.rt.moral_bias_id, aes(x=RT_moral_bias_match, y=RT_moral_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between RT of Matching and id categorization (moral-effect)") +
    apatheme
#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_moral2.pdf",out.type="cairo", width=8, height=6)
```

>>>>

pkgNeeded <- (c("tidyverse","plyr","ggplot2", "reshape2","ez", "bootES","MBESS", "BayesFactor","psych","corrplot"))

@@

```{r loadingData_e7,echo=FALSE,results='hide'}
df.L <- read.csv("df.Learn.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
df.T <- read.csv("df.Test.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
# render the numeric column
cols.num <- c("Age","Block","Bin","Trial","RT","Accuracy")
# Tcols.num <- c("SubjectID","Age","Block","Bin","Trial","RT","Accuracy")
df.L[cols.num] <- sapply(df.L[cols.num], as.numeric)
df.T[cols.num] <- sapply(df.T[cols.num], as.numeric)

@@

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1 <- df.L
df.T1 <- df.T
df.L1$RT <- df.L1$RT*1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000

@@

the effect of self on ACC
The correlation of accuracy between matching task and categrization based on morality criteria
```{r corr ACC_selfBias_between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
acc.self_bias_moral <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Valence_slf_oth_good)
df.acc.self_bias_moral <- df.corr.bias_acc[,c("L_acc_slf_oth_good","T_acc_Valence_slf_oth_good")]
colnames(df.acc.self_bias_moral) <- c("ACC_self_bias_match","ACC_self_bias_moral_categorization")
ggplot(df.acc.self_bias_moral, aes(x=ACC_self_bias_match, y=ACC_self_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between ACC of Matching and moral categorization (self-effect)") +
    apatheme
#ggsave("p_corr_acc_self1.eps", p_corr_acc_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_self1.pdf",out.type="cairo", width=8, height=6)
```

The correlation of accuracy between matching task and categrization based on identity criteria
```{r corr ACC_selfBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
acc.self_bias_id <- cor.test(df.corr.bias_acc$L_acc_slf_oth_good,df.corr.bias_acc$T_acc_Id_slf_oth_good)
df.acc.self_bias_id <- df.corr.bias_acc[,c("L_acc_slf_oth_good","T_acc_Id_slf_oth_good")]
colnames(df.acc.self_bias_id) <- c("ACC_self_bias_match","ACC_self_bias_id_categorization")
ggplot(df.acc.self_bias_id, aes(x=ACC_self_bias_match, y=ACC_self_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between ACC of Matching and id categorization (self-effect)") +
    apatheme
#ggsave("p_corr_acc_self2.eps", p_corr_acc_self2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_self2.pdf",out.type="cairo", width=8, height=6)
```

The effect of morality 
The correlation of accuracy between matching task and categrization based on morality criteria
```{r corr ACC_valBais between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
acc.moral_bias_moral <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Valence_good_bad_slf)
df.acc.moral_bias_moral <- df.corr.bias_acc[,c("L_acc_good_bad_slf","T_acc_Valence_good_bad_slf")]
colnames(df.acc.moral_bias_moral) <- c("ACC_moral_bias_match","ACC_moral_bias_moral_categorization")
ggplot(df.acc.moral_bias_moral, aes(x=ACC_moral_bias_match, y=ACC_moral_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm,fill = "gray") +   
    ggtitle("Correlation between ACC of Matching and moral categorization (moral effect)") +
    apatheme
#ggsave("p_corr_acc_moral1.eps", p_corr_acc_moral1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_moral1.pdf",out.type="cairo", width=8, height=6)
```

The correlation of accuracy between matching task and categrization based on identity criteria
```{r corr ACC_valBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
acc.moral_bias_id <- cor.test(df.corr.bias_acc$L_acc_good_bad_slf,df.corr.bias_acc$T_acc_Id_good_bad_slf)
df.acc.moral_bias_id <- df.corr.bias_acc[,c("L_acc_good_bad_slf","T_acc_Id_good_bad_slf")]
colnames(df.acc.moral_bias_id) <- c("ACC_moral_bias_match","ACC_moral_bias_id_categorization")
ggplot(df.acc.moral_bias_id, aes(x=ACC_moral_bias_match, y=ACC_moral_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm,fill = "gray") +   
    ggtitle("Correlation between ACC of Matching and id categorization (moral effect)") +
    apatheme
# ggsave("p_corr_acc_moral2.eps", p_corr_acc_moral2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_acc_moral2.pdf",out.type="cairo", width=8, height=6)
```

```{r corr RT_selfBias between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
rt.self_bias_moral <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Valence_slf_oth_good)
df.rt.self_bias_moral <- df.corr.bias_rt[,c("L_rt_m.slf_oth_good","T_rt_Valence_slf_oth_good")]
colnames(df.rt.self_bias_moral) <- c("RT_self_bias_match","RT_self_bias_moral_categorization")
ggplot(df.rt.self_bias_moral, aes(x=RT_self_bias_match, y=RT_self_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between RT of Matching and moral categorization (self-effect)") +
    apatheme
#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_self1.pdf",out.type="cairo", width=8, height=6)
```

```{r corr RT_selfBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
rt.self_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.slf_oth_good,df.corr.bias_rt$T_rt_Id_slf_oth_good)
df.rt.self_bias_id <- df.corr.bias_rt[,c("L_rt_m.slf_oth_good","T_rt_Id_slf_oth_good")]
colnames(df.rt.self_bias_id) <- c("RT_self_bias_match","RT_self_bias_id_categorization")
ggplot(df.rt.self_bias_id, aes(x=RT_self_bias_match, y=RT_self_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm,fill = "gray") +   
    ggtitle("Correlation between RT of Matching and id categorization (self-effect)") +
    apatheme
#ggsave("p_corr_RT_self2.eps", p_corr_RT_self2, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_self2.pdf",out.type="cairo", width=8, height=6)

@@

```{r corr RT_valBias between matching and categorization_val,echo=FALSE,warning=FALSE,message=FALSE }
rt.moral_bias_val <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Valence_good_bad_slf)
df.rt.moral_bias_moral <- df.corr.bias_rt[,c("L_rt_m.good_bad_slf","T_rt_Valence_good_bad_slf")]
colnames(df.rt.moral_bias_moral) <- c("RT_moral_bias_match","RT_moral_bias_moral_categorization")
ggplot(df.rt.moral_bias_moral, aes(x=RT_moral_bias_match, y=RT_moral_bias_moral_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) +   
    ggtitle("Correlation between RT of Matching and moral categorization (moral-effect)") +
    apatheme
#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_moral1.pdf",out.type="cairo", width=8, height=6)
```

```{r corr RT_valBias between matching and categorization_id,echo=FALSE,warning=FALSE,message=FALSE }
rt.moral_bias_id <- cor.test(df.corr.bias_rt$L_rt_m.good_bad_slf,df.corr.bias_rt$T_rt_Id_good_bad_slf)
df.rt.moral_bias_id <- df.corr.bias_rt[,c("L_rt_m.good_bad_slf","T_rt_Id_good_bad_slf")]
colnames(df.rt.moral_bias_id) <- c("RT_moral_bias_match","RT_moral_bias_id_categorization")
ggplot(df.rt.moral_bias_id, aes(x=RT_moral_bias_match, y=RT_moral_bias_id_categorization)) +
    geom_point() +    # Use hollow circles
    geom_smooth(method=lm) + 
    ggtitle("Correlation between RT of Matching and id categorization (moral-effect)") +
    apatheme
#ggsave("p_corr_RT_self1.eps", p_corr_RT_self1, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
dev.copy2pdf(file="p_corr_RT_moral2.pdf",out.type="cairo", width=8, height=6)
```
